##mi1
1. <- should be used instead of =
2.The unique() operation does not extract the unique value of x and y, hence the loop iterates through pmf value instead of sample space value
3.+ sign in the denominator of the log function is incorrect.
4.There should not be 3 for loops

##mi2
1.The for loop iterates the number of rows instead of the possible value of x and y should be taken
2.[[]] is not needed as x and y are vectors
3.The joint pmf value should not be the product of the marginals

##mi3
1.Forming data matrix is not necessary
2.The checking of equality is incorrect as it should be computing probability estimates.

```{r echo=FALSE}
telco <- readRDS("../data/telco.rds")
mi <- function(v1, v2) {
  v1_u <- unique(v1)
  v2_u <- unique(v2)
  I_xy <- 0
  for(x in v1_u) {
    p_x <- mean(v1 == x)
    for(y in v2_u) {
      p_xy <- mean(v1 == x & v2 == y)
      p_y <- mean(v2 == y)
      if(p_xy == 0) {
        next
      }
      I_xy <- I_xy + p_xy * log(p_xy / (p_x * p_y))
    }
  }
  I_xy
}
```
```{r}
x <- telco$Partner
y <- telco$Dependents
mi(x, y)
```

```{r echo=FALSE}
x <-seq(-2, 12, length=100)
y1 <- 2 * x/sqrt(x^2 + 1)
y2 <- x/2 - 3
plot(x, y1, type="l", ylim=c(-2, 3), ylab="y", main="Finding The Precise Root")
lines(x, y2)
points(10, 2, cex=5, col="red")
text(4.5, -1, expression(y == frac(x,2) - 3), pos=4)
text(0.5, 1, expression(y == frac(2*x, sqrt(x^2 + 1))), pos=2)
abline(h=0, lty=2)
```

```{r echo=FALSE}
x_start <- 8
f <- function(x) {2*x/sqrt(x^2 + 1) - x/2+3}
x <- x_start
while(abs(f(x))>1e-6){
  y <- 2*x/sqrt(x^2 + 1)
  x <- (y + 3)*2
}
x_final <- x
```

```{r}
uniroot(f, c(8, 11))$root
f2 <- function(x){5*x/sqrt(x^2 + 1) - x/2 + 3}
x <- seq(-10, 20, length=100)
y1 <- 5*x/sqrt(x^2 + 1)
y2 <- x/2 - 3
plot(x, y1, type="l")
lines(x, y2, type="l")
root_intervals <- list(c(-5, -2.5), c(-2.5, 0), c(12, 17))
f2_roots <- vapply(root_intervals, function(x)uniroot(f2, x)$root, 0.3)
```